NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-10-30 conclusions.tex
updated aaa figs with correct scale denomination, small fixes to setups, results and conclusions

\section{Conclusions}
\label{sec:conclusions}

We did good.

>>>>

\section{Conclusions}
\label{sec:conclusions}
Processes that involve vertices of three and four electroweak gauge bosons are among the most promising processes
where new physics might be found. Deviations from the Standard Model couplings or vertices that do not exist in the 
Standard Model might be found. The deviations from the Standard Model predictions can for instance conveniently be 
described by higher dimensional operators in terms of an effective field theory. Precise measurements of these  
processes allow to constrain and set limits to these higher dimensional operators.

In this paper we investigated the Standard Model predictions to a subset of such processes where we require
two photons plus an additional electroweak vector boson in the final state.  As additional vector boson we allowed
for a third photon as well as for a $W$ or $Z$ boson where we considered their leptonic decay modes.
This particularly implies that all off-shell and non-resonant contributions are taken into account.

We calculated the next-to-leading order QCD and electroweak corrections to these three processes for a set
of realistic fiducial cuts. Particular
emphasis has been put on the up to now unknown electroweak corrections as well as the combination of QCD and
electroweak corrections with the aim of producing the most precise prediction possible within the Standard Model.
As expected, we found the QCD corrections to be large and dominant compared to the electroweak corrections when 
calculating the corrections to the total cross sections. QCD corrections are particular large for these processes due to new
channels opening up at NLO but can effectively be reduced by applying a jet veto. Electroweak corrections
lead to moderate corrections to the total cross section of up to $4.4\%$ for the $\gamma\gamma \ell^{+}\ell^{-}$ 
process. However, in the high energy tail of differential distributions the electroweak corrections become increasingly important
and can lead to corrections of up to $30 \%$. Electroweak corrections become important in the same regions where one
also expects increasing effects of higher dimensional operators. The precise determination of limits on higher dimensional 
operators therefore requires the inclusion of higher order correction of both QCD as well as of the electroweak interaction.

### 2017-10-30 results.tex
updated aaa figs with correct scale denomination, small fixes to setups, results and conclusions

We define our central scales through
\begin{equation}
  \label{eq:murfdef}
  %\begin{split}
    \muR^0 = \muF^0 = %\left\{
    %\begin{array}{ll}
     % m_{\aaa} \qquad & \text{in \aaa\ production} \\[2mm]
      \tfrac{1}{2}\,H_T' \;. %& \text{in \aaw\ and \aaz\ production.}
    %\end{array}\right.
  %\end{split}
\end{equation}
In the case of the triple photon process $ H_\mathrm{T}' $ is just given by the scalar sum of all final state 
transverse momenta, for the two processes with the massive vector bosons it is defined as 
\begin{equation}
  \label{ew:defHT}
  \begin{split}
    H_\mathrm{T}' = E_\mathrm{T}^V + \sum_{\gamma,q,g} p_{\mathrm{T},i}
  \end{split}
\end{equation}
with $\left.E_\mathrm{T}^W\right.^2=(p_\ell+p_\nu)^2$ and 
$\left.E_\mathrm{T}^Z\right.^2=(p_{\ell^+}+p_{\ell^-})^2$ 
in full analogy to the case of the case of vector boson production 
in association with jets \cite{Berger:2009ep}.
As the Born process in each case has no $\muR$ dependence, we 
do not expect the choice of scale to have a significant influence 
on the size of the relative QCD and EW corrections.
We calculate the leading order cross section $\rd\sigma_\text{LO}(\muF)$, 
which only depends on the factorisation scale $\muF$, the 
NLO QCD differential correction factor $\deltaQCD(\muR,\muF)$, 
introducing the additional $\muR$-dependence, and the NLO EW 
differential correction factor $\deltaEW(\muF^0)$. 
To estimate the impact of yet to-be-calculated higher-order 
corrections we vary the free scales $\muR$ and $\muF$ 
by the conventional factor of two around their central values 
$\muR^0$ and $\muF^0$, respectively.
We do not vary the factorisation scale for the determination 
of $\deltaEW$ as the inherent, albeit normally phenomenologically 
irrelevant, stabilisation of the $\muF$-dependence at NLO EW 
is not reflected in our chosen PDF.
Hence, our NLO EW result exhibits the exact same $\muF$-dependence 
as the LO result.
We define 
\begin{equation}
  \label{eq:defnlo}
  \begin{split}
    \rd\sigma_\text{NLO QCD}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD\right)\\
    \rd\sigma_\text{NLO EW}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaEW\right)\\
    \rd\sigma_\text{NLO \QCDpEW}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD+\deltaEW\right)\\
    \rd\sigma_\text{NLO \QCDtEW}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD\right)\left(1+\deltaEW\right)\;.
  \end{split}
\end{equation}
Therein, the difference between NLO \QCDpEW\ and NLO \QCDtEW, which 
is of relative $\order(\alphas\alpha)$, can serve as an indicator 
of the potential size of unknown corrections at that order.

In Table \ref{tab:xsec} we quote the inclusive cross sections for all 
three processes. 
The fiducial cuts for each process is detailed in its 
respective subsection below. 
We note that the NLO QCD corrections for both triple photon 
production and \aaw\ production are strongly jet veto dependent, 
a result that was previously discussed in great detail in 
\cite{Bozzi:2011en,Bozzi:2011wwa}, and will be revisited in the 
following. 
A much milder jet veto dependence is found for \aaz\ production. 
The electroweak corrections to inclusive cross sections are 
generally much smaller, ranging from $0.6\%$ (\aaa) to $-1.8\%$ (\aaw) 
and $-4.4\%$ (\aaz).

>>>>

We define our central scales through
\begin{equation}
  \label{eq:murfdef}
  %\begin{split}
    \muR^0 = \muF^0 = %\left\{
    %\begin{array}{ll}
     % m_{\aaa} \qquad & \text{in \aaa\ production} \\[2mm]
      \tfrac{1}{2}\,H_T' \;. %& \text{in \aaw\ and \aaz\ production.}
    %\end{array}\right.
  %\end{split}
\end{equation}
In the case of the triple photon process $ H_\mathrm{T}' $ is just given by the scalar sum of all final state 
transverse momenta, for the two processes with the massive vector bosons it is defined as 
\begin{equation}
  \label{ew:defHT}
  \begin{split}
    H_\mathrm{T}' = E_\mathrm{T}^V + \sum_{\gamma,q,g} p_{\mathrm{T},i}
  \end{split}
\end{equation}
with $\left.E_\mathrm{T}^W\right.^2=(p_\ell+p_\nu)^2$ and 
$\left.E_\mathrm{T}^Z\right.^2=(p_{\ell^+}+p_{\ell^-})^2$ 
in full analogy to the case of the case of vector boson production 
in association with jets \cite{Berger:2009ep}.
As the Born process in each case has no $\muR$ dependence, we 
do not expect the choice of scale to have a significant influence 
on the size of the relative QCD and EW corrections.
We calculate the leading order cross section $\rd\sigma_\text{LO}(\muF)$, 
which only depends on the factorisation scale $\muF$, the 
NLO QCD differential correction factor $\deltaQCD(\muR,\muF)$, 
introducing the additional $\muR$-dependence, and the NLO EW 
differential correction factor $\deltaEW(\muF^0)$. 
To estimate the impact of yet-to-be-calculated higher-order 
corrections we vary the free scales $\muR$ and $\muF$ 
by the conventional factor of two around their central values 
$\muR^0$ and $\muF^0$, respectively.
We do not vary the factorisation scale for the determination 
of $\deltaEW$ as the inherent, albeit normally phenomenologically 
irrelevant, stabilisation of the $\muF$-dependence at NLO EW 
is not reflected in our chosen PDF.
Hence, our NLO EW result exhibits the exact same $\muF$-dependence 
as the LO result.
We define 
\begin{equation}
  \label{eq:defnlo}
  \begin{split}
    \rd\sigma_\text{NLO QCD}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD\right)\\
    \rd\sigma_\text{NLO EW}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaEW\right)\\
    \rd\sigma_\text{NLO \QCDpEW}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD+\deltaEW\right)\\
    \rd\sigma_\text{NLO \QCDtEW}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD\right)\left(1+\deltaEW\right)\;.
  \end{split}
\end{equation}
Therein, the difference between NLO \QCDpEW\ and NLO \QCDtEW, which 
is of relative $\order(\alphas\alpha)$, can serve as an indicator 
of the potential size of unknown corrections at that order.

In Table \ref{tab:xsec} we quote the inclusive cross sections for all 
three processes. 
The set of fiducial cuts for each process is detailed in its 
respective subsection below. 
We note that the NLO QCD corrections for both triple photon 
production and \aaw\ production are strongly jet veto dependent, 
a result that was previously discussed in great detail in 
\cite{Bozzi:2011en,Bozzi:2011wwa}, and will be revisited in the 
following. 
A much milder jet veto dependence is found for \aaz\ production. 
The electroweak corrections to inclusive cross sections are 
generally much smaller, ranging from $0.6\%$ (\aaa) to $-1.8\%$ (\aaw) 
and $-4.4\%$ (\aaz).

### 2017-10-30 setup.tex
updated aaa figs with correct scale denomination, small fixes to setups, results and conclusions

This combination of tools was previously used to calculate the 
NLO QCD corrections to \ldots \cite{} and the 
NLO EW corrections to for $\gamma\gamma+0,1,2\,\text{jets}$ production 
in \cite{Chiesa:2017gqx}.

>>>>

This combination of tools was previously used to calculate the 
NLO QCD corrections to $ZZ+\text{jet}$, $t\bar{t}+0,1\,\text{jets}$, 
$W^{+}W^{-}b\bar{b}$ and $h+0,1,2,3\,\text{jets}$ production 
in \cite{Binoth:2009wk,Hoeche:2013mua,Heinrich:2013qaa,
  Greiner:2015jha,Greiner:2016awe,Heinrich:2017bqp} and the 
NLO EW corrections to $\gamma\gamma+0,1,2\,\text{jets}$ production 
in \cite{Chiesa:2017gqx}.
